
#*************************************************************************
#*************************************************************************
## First Steps
## 1. Adding required Libraries
## 2. Connecting to DB
## 3. Fetching target table including GA events
#*************************************************************************
#*************************************************************************

```{r}
if(!"RMariaDB" %in% (.packages())){require(RMariaDB)}
install.packages("RMariaDB")
install.packages("doParallel")
install.packages("dplyr")
install.packages("zoo")
install.packages("ggplot2")
install.packages("tidyverse")


library(dplyr)
library(ggplot2)
library(RMariaDB)
library(jsonlite)
library(parallel)
library(foreach)
library(doParallel)
library(gridExtra)
library(tidyverse)  # get da whole shabeng!
#Connecting to MySQL DB
garageDB <- dbConnect(MariaDB()
                      , user = "user"
                      , password = "pass"
                      , dbname = "Dbname"
                      , host = "host",Port     = 3306)

#List tables in DB
dbListTables(garageDB)


# query <- "SELECT id,game_analytic_id,user_id,value,amount,amount_usd,DATE_FORMAT(FROM_UNIXTIME(`client_ts`), '%Y-%m-%d %H:%i:%s') as Date ,category,event_id from garajDb.data_final where DATE_FORMAT(FROM_UNIXTIME(`client_ts`), '%Y-%m-%d %H:%i:%s') > '2020-11-15' and category <> 'error' "

query<- "select id,game_analytic_id,user_id,value,amount,amount_usd,DATE_FORMAT(FROM_UNIXTIME(`client_ts`), '%Y-%m-%d %H:%i:%s') as Date ,category,event_id  from garajDb.Move_3mnth event_id not like 'Match3:Defeat:NumberOfInGameBoosterUsed:Ma%'    and event_id not like 'Match3:Win:NumberOfInGameBoosterUsed:Ma%'"
```





#*************************************************************************
As you know, Events are seperate by ':' charachter.
They all are located in "event_id"  field.

as very first step, I am trying to seperate this String into 5 distinct fields to ease later calculations: 
#*************************************************************************

```{r}
results <- dbSendQuery(garageDB, query)
df <- dbFetch(results)
dbClearResult(results)
# df<-2
df$lv1 <- unlist(mclapply(1:nrow(df),FUN = function(x){  strsplit(df$event_id[x] , ":")[[1]][1] } ,mc.cores = 20))
df$lv2 <- unlist(mclapply(1:nrow(df),FUN = function(x){  strsplit(df$event_id[x] , ":")[[1]][2] } ,mc.cores = 20))
df$lv3 <- unlist(mclapply(1:nrow(df),FUN = function(x){  strsplit(df$event_id[x] , ":")[[1]][3] } ,mc.cores = 20))
df$lv4 <- unlist(mclapply(1:nrow(df),FUN = function(x){  strsplit(df$event_id[x] , ":")[[1]][4] } ,mc.cores = 20))
df$lv5 <- unlist(mclapply(1:nrow(df),FUN = function(x){  strsplit(df$event_id[x] , ":")[[1]][5] } ,mc.cores = 20))


options("scipen"=100, "digits"=4)




head(df)

```


```{r}
colnames(gem_start)
```







#*************************************************************************
This event is activatd weekly on Thursdays
So I need to add a manipulated Week based "datetime" field, which starts on Thursday.
#*************************************************************************
```{r}

data.frame(day = 10:30,
week =unlist(lapply(10:30, function(x){format(as.POSIXct(paste0("2020-12-",x," 11:01:00 GMT")), "%U")}))
)


data.frame(day = 10:30,
week =unlist(lapply(10:30, function(x){format(as.Date(paste0("2020-12-",x," 11:01:00")) +3, "%U")}))
)


data.frame(day = p$datetime,
week =unlist(lapply(p$datetime, function(x){format(as.Date(x) +3, "%U")}))
)

p<- gem_start[(gem_start$user_id =="01b1e42a-6985-4314-8c93-580d4ec27646" & startsWith(gem_start$lv4, "Se")) ,c("datetime","lv4","week")]
p[order(p$datetime),]



```





#*************************************************************************
Here I take all logs of an Event, to show "starting Gems" which which user start Lux-levels

also I extract the followings:
serie_number: there are 10 Lux levels. I can extrcat it directly from "EVENT_ID"
#*************************************************************************
```{r}
gem_start <- df[startsWith(df$event_id , "Match3:FirstStart:Gem:"),]


gem_start$serie_number <-as.integer(substr(gem_start$lv4,21,22))
gem_start$datetime <- as.POSIXct(gem_start$Date, "%Y-%m-%d %H:%M:%S" ,tz = "GMT")
gem_start$week <- as.integer(strftime(gem_start$datetime,format="%Y"))*100+(as.integer(format(as.Date(gem_start$datetime)+3, "%U")) ) %%52 
gem_start$datetime


gem_start$datetime
# gem_start[,c("datetime","week")]
```












#*************************************************************************
user can go to normal levels and then comes back to Lux.
here I try to detect how many times did he leave the Lux by identifying last level played.
It canbe eauther another "lux" level (gamer never leaves the series) or "normal" (gamer jumped out)
I do itusing lag function
#*************************************************************************

```{r}
##### last level
s1<-gem_start %>%
group_by(user_id) %>%
mutate(last_level= lag(lv4, order_by=Date)
       )
```




#*************************************************************************
An aggregation showing starting and finishing GEMs for each User, on each level, on each week
```{r}
s2<- s1 %>%
  filter(str_detect(lv4, "^Ser")) %>%
  group_by(user_id) %>%
  mutate(gem_start = as.integer(value ),
       gem_finish= as.integer(lead(value, order_by=Date) ),
       start_time = datetime,
       finish_time = lead(datetime, order_by=Date)
  ) %>%
  mutate(gem_spend = ifelse( gem_start >gem_finish  , gem_finish -  gem_start,0 ) ,
       gem_recieved = ifelse( gem_start <gem_finish  ,  gem_start - gem_finish,0 ) ,   
       level_dur_min =  as.numeric(difftime(as.POSIXct(finish_time),as.POSIXct(start_time) ,units = "mins" )),
       level_dur_hour = as.numeric( difftime(as.POSIXct(finish_time),as.POSIXct(start_time) ,units = "hours" ))
  )


base <- s2 %>% select("user_id","value","lv4", "week", "last_level","gem_start","gem_finish","start_time","finish_time", "Date","gem_spend", "level_dur_min", "level_dur_hour") %>%
  arrange(user_id,Date)


base$serie_number <-as.integer(substr(base$lv4,21,22))
base
```











#*************************************************************************
###################  Energy purchased
filtering GA logs belong to energy purchased Event on Lux levels
aggregation  showing  energy-puchased-cnt, for each user,on each level, on each week
#*************************************************************************
```{r}


user_energy <- df[startsWith(df$event_id , "Match3:Win:Energy:S"),]
user_energy$serie_number <-as.integer(substr(user_energy$lv4,21,22))
user_energy$datetime <- as.POSIXct(user_energy$Date, "%Y-%m-%d %H:%M:%S" ,tz = "GMT")
user_energy$week <- as.integer(strftime(user_energy$datetime,format="%Y"))*100+(as.integer(format(as.Date(user_energy$datetime)+3, "%U")) ) %%52 

user_energy

user_energy_cnt <- user_energy %>% group_by(user_id,serie_number,week) %>%
  summarise(
      energy_cnt = n()
    ) 

user_energy_cnt
nrow(user_energy_cnt)  #16608
sum(user_energy_cnt$energy_purchased_cnt)  #27892


```


<!-- ################# move left -->
<!-- ```{r} -->


<!-- user_energy <- df[startsWith(df$event_id , "Match3:Win:Energy:S"),] -->
<!-- user_energy$serie_number <-as.integer(substr(user_energy$lv4,21,22)) -->
<!-- user_energy$datetime <- as.POSIXct(user_energy$Date, "%Y-%m-%d %H:%M:%S" ,tz = "GMT") -->
<!-- user_energy$week <- as.integer(strftime(user_energy$datetime,format="%Y"))*100+(as.integer(format(as.Date(user_energy$datetime)+3, "%U")) ) %%52  -->

<!-- user_energy -->

<!-- user_energy_cnt <- user_energy %>% group_by(user_id,serie_number,week) %>% -->
<!--   summarise( -->
<!--       energy_cnt = n() -->
<!--     )  -->

<!-- user_energy_cnt -->
<!-- nrow(user_energy_cnt)  #16608 -->
<!-- sum(user_energy_cnt$energy_purchased_cnt)  #27892 -->


<!-- ``` -->


#*************************************************************************
################# Booster purchased (defeat)
filtering GA logs belong to Booster purchased Event on Lux levels, where user is defeated
aggregation  showing  booster-puchased-cnt, for each user,on each level, on each week
#*************************************************************************
```{r}
lux_boost_purchased_d <- df[startsWith(df$event_id , "Match3:Defeat:NumberOfInGameBoosterUsed:S"),]
lux_boost_purchased_d$serie_number <-as.integer(substr(lux_boost_purchased_d$lv4,21,22))
lux_boost_purchased_d$datetime <- as.POSIXct(lux_boost_purchased_d$Date, "%Y-%m-%d %H:%M:%S" ,tz = "GMT")
lux_boost_purchased_d$week <- as.integer(strftime(lux_boost_purchased_d$datetime,format="%Y"))*100+(as.integer(format(as.Date(lux_boost_purchased_d$datetime)+3, "%U")) ) %%52 

lux_boost_purchased_d

user_boost_defeat_pch_cnt <- lux_boost_purchased_d %>% group_by(user_id,serie_number,week) %>%
  summarise(boost_defeat_purchased_cnt = n(),boost_defeat_purchased_sum=sum( as.integer(value)))




user_boost_defeat_pch_cnt
length(unique(user_boost_defeat_pch_cnt$user_id))    #5964
nrow(user_boost_defeat_pch_cnt)  #23400
sum(user_boost_defeat_pch_cnt$boost_purchased_cnt)  #36187
sum(user_boost_defeat_pch_cnt$boost_purchased_sum)    #551



```





#*************************************************************************
################# Booster purchased (win)
filtering GA logs belong to Booster purchased Event on Lux levels, where user is won
aggregation  showing  booster-puchased-cnt, for each user,on each level, on each week
#*************************************************************************
```{r}
lux_boost_purchased_w <- df[startsWith(df$event_id , "Match3:Win:NumberOfInGameBoosterUsed:S"),]
lux_boost_purchased_w$serie_number <-as.integer(substr(lux_boost_purchased_w$lv4,21,22))
lux_boost_purchased_w$datetime <- as.POSIXct(lux_boost_purchased_w$Date, "%Y-%m-%d %H:%M:%S" ,tz = "GMT")
lux_boost_purchased_w$week <- as.integer(strftime(lux_boost_purchased_w$datetime,format="%Y"))*100+(as.integer(format(as.Date(lux_boost_purchased_w$datetime)+3, "%U")) ) %%52 

lux_boost_purchased_w

user_boost_win_pch_cnt <- lux_boost_purchased_w %>% group_by(user_id,serie_number,week) %>%
  summarise(boost_win_purchased_cnt = n(),boost_win_purchased_sum=sum( as.integer(value)))




user_boost_win_pch_cnt
length(unique(user_boost_win_pch_cnt$user_id))    #5964
nrow(user_boost_win_pch_cnt)  #23400
sum(user_boost_win_pch_cnt$boost_purchased_cnt)  #36187
sum(user_boost_win_pch_cnt$boost_purchased_sum)    #551



```




#*************************************************************************
################# move purchased

filtering GA logs belong to extra Move purchased Event on Lux levels
aggregation  showing  Extra-move-puchased-cnt, for each user,on each level, on each week
#*************************************************************************
```{r}
lux_mv_purchased <- df[startsWith(df$event_id , "Match3:MovePurchased:Se"),]
lux_mv_purchased$serie_number <-as.integer(substr(lux_mv_purchased$lv3,21,22))
lux_mv_purchased$datetime <- as.POSIXct(lux_mv_purchased$Date, "%Y-%m-%d %H:%M:%S" ,tz = "GMT")
lux_mv_purchased$week <- as.integer(strftime(lux_mv_purchased$datetime,format="%Y"))*100+(as.integer(format(as.Date(lux_mv_purchased$datetime)+3, "%U")) ) %%52 



user_mv_pch_cnt <- lux_mv_purchased %>% group_by(user_id,serie_number,week) %>%
  summarise(mv_purchased_cnt = n())




user_mv_pch_cnt
nrow(user_mv_pch_cnt)  #5073
sum(user_mv_pch_cnt$mv_purchased_cnt)  #9846


```






#*************************************************************************
###################  Defeat
target: retry cnt on each level. How many time did a user retried a LUX-level?
filtering GA logs belong to defeat  Event on Lux levels.
aggregation  showing  defeat-cnt, for each user,on each level, on each week
#*************************************************************************
```{r}

df[startsWith(df$event_id , "Match3:Defeat:S"),]

user_defeat <- df[startsWith(df$event_id , "Match3:Defeat:S"),]
user_defeat$serie_number <-as.integer(substr(user_defeat$lv3,21,22))
user_defeat$datetime <- as.POSIXct(user_defeat$Date, "%Y-%m-%d %H:%M:%S" ,tz = "GMT")
user_defeat$week <- as.integer(strftime(user_defeat$datetime,format="%Y"))*100+(as.integer(format(as.Date(user_defeat$datetime)+3, "%U")) ) %%52 

user_defeat_cnt <- user_defeat %>% group_by(user_id,week,serie_number) %>%
  mutate(start_time = datetime,finish_time = lead(datetime, order_by=Date)) %>%
summarise( 
    defeat_cnt = n() 
) %>%
  mutate(   
       defeat_dur_min =  as.numeric(difftime(as.POSIXct(finish_time),as.POSIXct(start_time) ,units = "mins" )),
       defeat_dur_hour = as.numeric( difftime(as.POSIXct(finish_time),as.POSIXct(start_time) ,units = "hours" ))
  )

user_defeat_cnt


```


```{r}

p<-user_defeat[(user_defeat$user_id =="01b1e42a-6985-4314-8c93-580d4ec27646" ) ,c("datetime","lv3","week")]
p[order(p$datetime),]

p<-user_defeat_cnt[(user_defeat_cnt$user_id =="01b1e42a-6985-4314-8c93-580d4ec27646" ), ]
# p[order(p$datetime),]
p
# gem_start$
```












################## Creating the 360-degree Lux-Fact***********************
#*************************************************************************
#*************************************************************************
##    joining all the above dataframes
##    Granularity: USER , Level, week
##    adding some metrics to enhace later analysis based on existing fields:
##    last_energy_cnt 
##    enrgey_purchased flag 
##    lux_start time
##    lux_finish time
##    max_level_reached on lux levels
##    lux_gem_start
##    lux_gem_finish
##    avg_lv_dur_min: avg duration time of each Luxury level for each level
##    median_lv_dur_min
##    last_lv_dur_min: duration of very last level that user played in Lux series. (showing how hard the last level was, which made some gamers quite)
##    tot_defeat_cnt
##    last_defeat_cnt:  how many times did the gamer lose on last level? (showing how hard the last level of gamed n that serie was)
##    moreto come...
#*************************************************************************
#*************************************************************************

```{r}

j1<- base %>% 
  left_join( user_defeat_cnt, c("user_id" = "user_id", "serie_number" ="serie_number","week"="week")) %>%
  left_join( user_mv_pch_cnt, c("user_id" = "user_id", "serie_number" ="serie_number","week"="week")) %>%
  left_join( user_boost_defeat_pch_cnt, c("user_id" = "user_id", "serie_number" ="serie_number","week"="week")) %>%
  left_join( user_boost_win_pch_cnt, c("user_id" = "user_id", "serie_number" ="serie_number","week"="week")) %>%
  left_join( user_energy_cnt, c("user_id" = "user_id", "serie_number" ="serie_number","week"="week"))

j1
  


j1$jump_out<-  apply(j1 , MARGIN = 1 , FUN = function(x){ifelse(startsWith(x[5],"Match3"),as.integer(x[14]),NA)}  )

j2 <- j1 %>% group_by(user_id) %>% mutate(last_energy_cnt = lag(energy_cnt,order_by = Date))

j3 <-j2 %>% mutate(enrgey_purchased = ifelse( (last_energy_cnt - energy_cnt >0) & jump_out ==0 ,(last_energy_cnt - energy_cnt) ,0 ))

j3
# j4 <- 
  j3[,c("user_id" ,"serie_number","week","energy_cnt","last_energy_cnt" , "enrgey_purchased")]

```

```{r}

j4 <- j3 %>%   mutate(lux_gem_start = ifelse(serie_number ==1 , as.integer(value),0))

j5 <- j4 %>% group_by(user_id,week) %>% mutate(reverese_rnk = row_number(-serie_number)) %>%
  mutate(lux_gem_finish = ifelse(reverese_rnk ==1 , as.integer(value),0))
j5[,c("user_id","week","serie_number","level_dur_min","level_dur_hour","lux_gem_start","reverese_rnk","lux_gem_finish","defeat_cnt","defeat_dur_min","defeat_dur_hour")]


j5
fact <- j5 %>% group_by(user_id,week) %>%
  summarise( lux_start  = min(Date),
             lux_finish = max(Date),
             max_level_reached   = max(serie_number),
             lux_gem_start       = max(lux_gem_start),
             lux_gem_finish      = max(lux_gem_finish),
             avg_lv_dur_min      = mean(level_dur_min),
             median_lv_dur_min   = median(level_dur_min),
             last_lv_dur_min     = max(ifelse(reverese_rnk==1 , level_dur_min ,0 )),
             tot_defeat_cnt      = sum(defeat_cnt,na.rm = TRUE),
             last_defeat_cnt     = max(ifelse(reverese_rnk==1 , defeat_cnt ,0 ))
             ) 
  mutate(lux_gem_balance = lux_gem_finish - lux_gem_start)

j5
fact

#### why tot_defeat_cnt is more than 3???? 
```





#*************************************************************************
#*************************************************************************
#***  
#***  Asking some questions from the fact
#***
#***  attraction: do they finish the game? where do they stop by? 
#***  does spending more money ends up in not leaving the level? or that makepoeple stay on the game?
#***  
#***  do people leave bcz it's so easy? or hard? does that help retention to  make levels harder?
#***  
#***  
#***  do they leave after reaching the prise?
#***  
#***  do they buy more in LUX?
#***  do they stay more in LUX?
#***  do they retry more in LUX?
#***  
#***  do they jump out usually?  if yes that meansit is not attractive enough
#***  do they jump to get GEM?
#***  
#***  why dothey leav? 
#***  1. ENERGY?   then dothey come back when energy is full?
#***  2. retry threshold?
#***  3. boring?  (leave onvery first levels)
#***  4. they reach the firt prise?
#***  5. normal game is more interesting?  (they jump  a lot)
#***  
#***  Segmenting
#***  
#***  Does starting Gem effect who much they go in?
#***  
#***  
#***  is it beneficial  for the? is the ending GEM more than Starting GEM?
#***  
#*************************************************************************
#*************************************************************************










############################################### more to come


######## LEVEL 360-degree FACT ( LEVEL UNDERSTANDING)
```{r}
user_startgem_lst_lv %>%
  group_by(user_id,week) %>%
  summarise()


```



####### #USER UNDERSTAND

```{r}

```



####### LEVEL DIFUCULTY IN NORMAL GAMES
